\documentclass[12pt]{report}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{color}
\usepackage{lettrine}
\usepackage{textcomp}
\usepackage[utf8]{inputenc}
\usepackage[toc,page]{appendix}
\usepackage{courier}

\usepackage[margin=2cm]{geometry}

\definecolor{dgrey}{rgb}{0.3,0.3,0.3}
\definecolor{dyellow}{rgb}{0.6,0.6,0.0}
\definecolor{gblue}{rgb}{0.35,0.35,0.6}

\hypersetup{
	colorlinks=true,
	linktoc=all,
	linkcolor=gblue,
	citecolor=dyellow,
}

\lstset{basicstyle=\ttfamily\footnotesize, frame=single,
breaklines=true,showstringspaces=false,numbers=left}

\title{ECSE 323 - Digital System Design\\After Action Report - The Dealer Finite State Machine}
\author{Harley Wiltzer (260690006)\\Spiros-Daniel Mavroidakos (260689391)}
\date{March 30, 2017}

\begin{document}
\pagenumbering{gobble}
\maketitle
\newpage
\pagestyle{fancy}
\fancyhf{}
\rhead{Harley Wiltzer (260690006), Spiros-Daniel Mavroidakos (260689391) - Vandelay Industries}
\pagenumbering{arabic}
\tableofcontents

\part{A Pleasant Preamble}
\lettrine{S}ometimes in life, one may be presented with situations that make him rethink his beliefs and
question who, in fact, he really is. It is moments like these that actually define an individual
\textit{ad postremum}. Of course, it is up to the individual in question to \textit{realize} that he shall be
withdrawing cathexis from the myriad objects of empirical reality around him if enlightenment should
be obtained. People that occasionally experience this enlightenment are called patricians. Those who
continuously experience this enlightenment are called Engineers.\\\\
Consider the infamous game of Blackjack. Some may enjoy this game as a nice way to pass the time,
others may be violently obsessed with it. Regardless of who is playing, the game can only be played
reliably when players understand and follow the rules and when a credible dealer is present.
Naturally, the players are needed for the game to be played, and of course the game is only really
\textit{being played} when the rules are followed. The presence of the dealer, however, is far more
interesting than what the uninformed reader may believe.\\\\
Some say the dealer's job is to deal the cards, but that is a vast and decadent oversimplification.
Sure, the dealer \textit{should} deal the cards (at the appropriate times, that is), but the dealer
is also responsible for establishing structure and ensuring that the game does not get out of hand.
In fact, the rules of the game themselves have their strings pulled by the dealer. \\But some dealers
do not follow the rules.\\\\
It is no longer news that the goal of these laboratory sessions is to build a \textit{crazy eights}
game, and not a Blackjack game. Although the rules of the two games are different, both take on the
rules-dealer paradigm of gameplay. The layman, and even the patrician, may focus on the rules of the
game principally. However, as Engineers, the main focus of this laboratory was to create not just a
functional dealer, but a reliable, ethical, and ultimately compliant dealer. As shown later in this
report, this was successfully accomplished due to the design of a clever \textit{finite state
machine}, a construct that has also been used in the design of underwhelming robots.\\\\
In the interest of moral behavior, it would be unethical to display the accomplishments of this
laboratory session without giving due credit to the Altera Quartus II and Modelsim software, whose
magical functionalities allow such complex designs to be mapped onto an FPGA. Given Altera's great
text editing accomodations and incredible timing simulation tools, the development of this system
was dream-like.\\\\
At this stage, the reader is invited to explore the remainder of this report, which will go through
in a (hopefully) simple and organized manner the discoveries made during this laboratory session.
Beyond that, this report will discuss \textit{how} these discoveries were made, and how they were
reinforced, so the reader may gain intuition on developing state of the art digital systems.\\\\
Please enjoy the discoveries and details that follow, and try to learn something from them. Much is
to be gained
by grasping the concepts of the rules-dealer paradigm, as they apply to more in life than simply
digital systems and card games. To conclude this pleasant preamble, the reader is encouraged to,
above all, \textit{have fun} with this report, and better yet, to have fun with life. Finally, it is
important to remember that while by law a man is guilty for violating the rules, in ethics a man is
guilty merely by \textit{considering} such violation. Be careful, be wise, and Baba Booey to all.

\end{document}
